Title: Ecosystem size and complexity dictate riverine biodiversity

### 2021-03-08 manuscript_science.Rmd
Update manuscript_science.Rmd

Our theoretical analysis yielded results consistent with our prediction. Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**). The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios. Importantly, the impact of ecosystem complexity was comparable to that of ecosystem size (**Figures 2 and 3**); therefore, they play equally-important roles in regulating biodiversity. The strength of competition and dispersal processes (dispersal distance and probability) did not change the relationships between $\gamma$ diversity and ecosystem properties (compare panels in **Figures 2 and 3**). Hence, the ecosystem size and complexity are expected to increase $\gamma$ diversity regardless of ecological scenarios.

>>>>

Our theoretical analysis yielded results consistent with our prediction. Ecosystem size and complexity both increased $\gamma$ diversity under a realistic landscape scenario (**Figures 2 and 3**), where the environmental variation at headwaters $\sigma_h$ is greater than the degree of local environmental noise $\sigma_l$ (**Figure 1A**). The relationships had a characteristic of power-law (i.e., linear in a log-log scale) and were consistent under various ecological scenarios (compare panels in **Figures 2 and 3**). Importantly, the impact of ecosystem complexity was comparable to that of ecosystem size. Hence, the ecosystem size and complexity play equally important roles in regulating $\gamma$ diversity regardless of ecological scenarios.
